### 2022-09-30 inst/Examples/Paper_results/Paper_results_1.Rmd
Reimplementing features (part 1)

We also import table XXXX from Myrvoll-Nilsen et al. (2022) which gives suitable data windows for each abrupt warming transition that is analysed. This was found by varying the start and end point over a 2-dimensional grid and picking those where the noise in the linear ramp model yielded the lowest amplitude.

@@

```{r events_import, eval=TRUE}
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`
buizert_onsets = read_excel("inst/Examples/Paper_results/data/Buizert_onsets.xlsx",
                            col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]
capron_onsets_NGRIP_d18O = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                           sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`
capron_onsets_NGRIP_dust = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                                sheet="Ca2+",n_max=24)
capron_ages_NGRIP_dust = capron_onsets_NGRIP_dust$`t1 (50%)`
capind = numeric(29); buiind = numeric(29)
capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

@@

  control.linramp = list(proxy=proxy,interval=interval_d18O,interval.unit="index",
                         depth.ref=depth.reference, imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         silent=2L,
                         label=paste0(eventnumber," (d18O):", event_intervals[eventnumber,2])
                         )

  control.linramp_dust = list(proxy=logdust,interval=interval_dust,interval.unit="index",
                         depth.ref=depth.reference, imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         silent=2L,
                         label=paste0(eventnumber," (logCa):", event_intervals[eventnumber,2])
                         )

>>>>

We also import table D1 from Myrvoll-Nilsen et al. (2022) which gives suitable data windows for each abrupt warming transition that is analysed. This was found by varying the start and end point over a 2-dimensional grid and picking those where the noise in the linear ramp model yielded the lowest amplitude.

@@

```{r events_import, eval=TRUE}
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`
# buizert_onsets = read_excel("inst/Examples/Paper_results/data/Buizert_onsets.xlsx",
#                             col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]
# capron_onsets_NGRIP_d18O = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
#                            sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`
# capron_onsets_NGRIP_dust = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
#                                 sheet="Ca2+",n_max=24)
capron_ages_NGRIP_dust = capron_onsets_NGRIP_dust$`t1 (50%)`
capind = numeric(29); buiind = numeric(29)
capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

@@

  control.linramp = list(proxy=proxy,interval=interval_d18O,interval.unit="index",
                         depth.ref=depth.reference, #imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         silent=2L,
                         label=paste0(eventnumber," (d18O):", event_intervals[eventnumber,2])
                         )

  control.linramp_dust = list(proxy=logdust,interval=interval_dust,interval.unit="index",
                         depth.ref=depth.reference, #imp.fit=imp.fits[eventnumber],
                         h=steplengths[eventnumber],
                         opt.params=opt.params,
                         priorparams=priorparams,
                         silent=2L,
                         label=paste0(eventnumber," (logCa):", event_intervals[eventnumber,2])
                         )
